Dark matter halo concentrations with a bayesian approach

### 2014-09-09 paper/article.tex
some edits

\begin{equation}
\rho(r) = \frac{\rho_c\delta_c}{r/r_s(1+r/r_s)^2}, 
\end{equation}
%
where $\rho_c\equiv 3H^2/8\pi G$ is the Universe critical density,
$\delta_c$ is the halo dimensionless characteristic density and $r_s$
is known as the scale radius, the radius that marks the transition
between the two power law behaviour in the $\rho\propto r^{-1}$ for
$r<r_s$ and $\rho\propto r^{-2}$ for  $r>r_s$.

We define the virial radius of a halo, $r_v$, as the boundary of the
spherical volume that encloses an average density of $\Delta_h$ times
the average density of the Universe. The corresponding mass $M_{v}$,
the virial mass, can be thus expressed as $M_{v} =
\frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.

The total mass enclosed within a radius $r$ can be computed to be:
\begin{equation}
M(<r) = 4\pi\rho_c\delta_c  r_s^3\left[\ln \left
  (\frac{r_s+r}{r}\right) - \frac{r}{r_s+r}\right].
\end{equation}

We can now define the concentration of the halo as $c=r_v/r_s$, the
dimensioless variable $x\equiv r/r_v$ and $m\equiv M(<r)/M_v$, which
allows us to express the total enclosed mass within a dimensionless
radius $x$ as:

\begin{equation}
m(<x) =
\frac{1}{A}\left[\ln\left(1+xc\right)-\left(\frac{xc}{xc+1}\right)\right],
\label{eq:profile}
\end{equation}
%
where 
%
\begin{equation}
A=\left[\ln\left(1+c\right)-\left(\frac{c}{c+1}\right)\right],
\end{equation}

meaning that the concentration is the only free parameter to
determine the density profile of the halo. In Figure
\ref{fig:profiles} we show the family of normalized integrated mass
profiles for different values of the concentration in the range
$1\leq c \leq 20$.

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
\end{center}
\caption{Mass profiles of several haloes with different concentrations
    \label{fig:profiles}}
\end{figure}

>>>>

\begin{equation}
\rho(r) = \frac{\rho_c\delta_c}{r/r_s(1+r/r_s)^2}, 
\end{equation}
%
where $\rho_c\equiv 3H^2/8\pi G$ is the Universe critical density,
$\delta_c$ is the halo dimensionless characteristic density and $r_s$
is known as the scale radius, the radius that marks the transition
between the two power law behaviour in the $\rho\propto r^{-1}$ for
$r<r_s$ and $\rho\propto r^{-3}$ for  $r>r_s$.

We define the virial radius of a halo, $r_v$, as the boundary of the
spherical volume that encloses an average density of $\Delta_h$ times
the average density of the Universe. The corresponding mass $M_{v}$,
the virial mass, can be written as $M_{v} =
\frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.

\subsection{Integrated Mass}
From these definitions we can compute the total mass enclosed inside a
radius $r$:
\begin{equation}
M(<r) = 4\pi\rho_c\delta_c  r_s^3\left[\ln \left
  (\frac{r_s+r}{r}\right) - \frac{r}{r_s+r}\right].
\end{equation}

We can now express the same quantity in terms of dimensionless the
variables $x\equiv r/r_v$ and $m\equiv M(<r)/M_v$,
%
\begin{equation}
m(<x) =
\frac{1}{A}\left[\ln\left(1+xc\right)-\left(\frac{xc}{xc+1}\right)\right],
\label{eq:profile}
\end{equation}
%
where 
%
\begin{equation}
A=\left[\ln\left(1+c\right)-\left(\frac{c}{c+1}\right)\right],
\end{equation}
%
and the parameter $c$ is known as the concentration $c\equiv r_v/r_s$.

The most interesting feature of Eq. (\ref{eq:profile}) is that the
concentration is the only free parameter to describe the shape of the
halo densitry profile. In Figure \ref{fig:profiles} we show $m(<x)$ as
a function of $x$ for different values of the concentration in the range
$1\leq c \leq 20$.

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
\end{center}
\caption{Dimensionless mass profiles as a function of the
  dimensionless radius for different concentration values.
    \label{fig:profiles}}
\end{figure}

\subsection{Circular velocity}

It is also customary to express the mass of the halo inte terms of the
circular velocity $V_{c}=sqrt{GM(<r)/r}$. From this we can
define a new dimensionless circular velocity $v(<x)\equiv
V_{c}(<r)/V_{c}(<r_v)$, using the result in Equation \ref{eq:profile}
to have:

\begin{equation}
v(<x)=\sqrt{\frac{1}{A}\left[\frac{\ln\left(1+xc\right)}{x}-\frac{c}{xc+1}\right]},
\end{equation}
